Testing atlantisom: true biomass output from Atlantis

### 2019-04-26 TrueBioTest.Rmd
formatting, try NOBA

In this example, we have a local folder "atlantisoutput" with three subdirectories:
  * "CalCurrentSummitScenario1": California Current Atlantis model output
  * "NEUStest20160303": older (broken) Northeast US Atlantis model output
  * "NOBACERESGlobalSustainability": Norwegian-Barents Sea Atlantis model output

@@

initCCA <- FALSE
initNEUS <- TRUE
initNOBA <- FALSE

@@

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  functional.groups.file <- "nordic_groups_v04.csv" 
  biomass.pools.file <- "nordic_biol_v23.nc"
  biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
  box.file <- "Nordic02.bgm"
  initial.conditions.file <- "nordic_biol_v23.nc"
  run.prm.file <- "nordic_run_v01.xml"
  scenario.name <- "nordic_runresults_01"
}

@@

```{r get_truth, message=FALSE, warning=FALSE, eval = FALSE}
#Store all loaded results into an R object
results <- run_truth(scenario = scenario.name,
          dir = d.name,
          file_fgs = functional.groups.file,
          file_bgm = box.file,
          select_groups = funct.group.names,
          file_init = initial.conditions.file,
          file_biolprm = biol.prm.file,
          file_runprm = run.prm.file
)

@@

Now the R object `results` with the comprehensive results from the Atlantis model has been read in. It is also saved as an .RData file titled "output[scenario.name]run_truth.RData" in the directory with the model output, so that later analyses can use `load()' instead of taking the time to rerun `atlantisom::run_truth()'.

@@

This section tests the `atlantisom::create_survey()' and `atlantisom::sample_survey_biomass()' functions by comparing a census (survey sampling everything) with the results generated by `atlantisom::run_truth()' above.

@@

```{r census-spec, message=FALSE, warning=FALSE}

@@

Because the results of `run_truth' provide both biomass at age and numbers at age, we can use `create_survey' on both with some modifications.

>>>>

In this example, we have a local folder "atlantisoutput" with three subdirectories:

  * "CalCurrentSummitScenario1": California Current Atlantis model output
  * "NEUStest20160303": older (broken) Northeast US Atlantis model output
  * "NOBACERESGlobalSustainability": Norwegian-Barents Sea Atlantis model output

@@

initCCA <- FALSE
initNEUS <- FALSE
initNOBA <- TRUE

@@

if(initNOBA){
  d.name <- here("atlantisoutput","NOBACERESGlobalSustainability")
  functional.groups.file <- "nordic_groups_v04.csv" 
  biomass.pools.file <- "nordic_biol_v23.nc"
  biol.prm.file <- "nordic_biol_incl_harv_v_007_3.prm"
  box.file <- "Nordic02.bgm"
  initial.conditions.file <- "nordic_biol_v23.nc"
  run.prm.file <- "nordic_run_v01.xml"
  scenario.name <- "nordic_runresults_01"
}
# NOBA note: output filenames in CCA and NEUS begin with "output" and the run_truth function is written to expect this. Need to check if default Atlantis output file nomenclature has changed or if NOBA is a special case. For now, NOBA filenames have been changed to include prefix "output"
```

@@

```{r get_truth, message=FALSE, warning=FALSE}
#Store all loaded results into an R object
results <- run_truth(scenario = scenario.name,
          dir = d.name,
          file_fgs = functional.groups.file,
          file_bgm = box.file,
          select_groups = funct.group.names,
          file_init = initial.conditions.file,
          file_biolprm = biol.prm.file,
          file_runprm = run.prm.file
)

@@

Now the R object `results` with the comprehensive results from the Atlantis model has been read in. It is also saved as an .RData file titled "output[scenario.name]run_truth.RData" in the directory with the model output, so that later analyses can use 'load()' instead of taking the time to rerun `atlantisom::run_truth()'.

@@

This section tests the `atlantisom::create_survey()` and `atlantisom::sample_survey_biomass()` functions by comparing a census (survey sampling everything) with the results generated by `atlantisom::run_truth()` above.

@@

```{r census-spec, message=FALSE, warning=FALSE, eval=FALSE}

@@

Because the results of `run_truth` provide both biomass at age and numbers at age, we can use `create_survey` on both with some modifications.
